Andres Karjus &nbsp;<font size='3'> evolutionary&nbsp;linguist | cultural&nbsp;data&nbsp;analytics&nbsp;scholar | digital&nbsp;humanities&nbsp;instructor </font>

### 2023-02-19 cudan/paperplots.qmd
profile update

tops = attr(festgenrevecs, "tops") %>% 
  left_join(festgenrevecs %>% filter(!duplicated(EventID_VZ)), by="EventID_VZ") %>% 
  select(txtKind, s, EventID_VZ, libelleFestival_NEW_VZ, YearEvent, LibelleEvent_NEW_VZ) %>% 
  filter(libelleFestival_NEW_VZ %in% exgenfests) %>% 
  filter(YearEvent==2019) %>% 
  ungroup() %>% 
  mutate(colorgenre=case_when(txtKind%in% levels(festgenrevecs$colorgenre)~txtKind, T~"...")) %>% 
  mutate(colorgenre2=fct_relevel(as.factor(colorgenre), 
                                levels(festgenrevecs$colorgenre) %>% gsub("other","...",.)))

ggplot(tops, aes(x=colorgenre2, y=s, fill=colorgenre2))+
  geom_bar(stat="identity", width=1, color=NA)+
  scale_fill_manual(values=sixgcols)+
  #coord_cartesian(expand = 0, ylim=c(0,100))+
  theme_void()+
  theme(axis.title = element_blank(),
        legend.position = "none",
        panel.border  = element_rect(size=0.5, color="gray10", fill=NA)
        )+
  facet_wrap(~libelleFestival_NEW_VZ, strip.position="bottom", scales = "free", nrow=2)

>>>>

tops = attr(festgenrevecs, "tops") %>% 
  left_join(festgenrevecs %>% filter(!duplicated(EventID_VZ)), by="EventID_VZ") %>% 
  select(txtKind, s, EventID_VZ, libelleFestival_NEW_VZ, YearEvent, LibelleEvent_NEW_VZ) %>% 
  filter(libelleFestival_NEW_VZ %in% exgenfests) %>% 
  filter(YearEvent==2019) %>% 
  ungroup() %>% 
  mutate(colorgenre=case_when(txtKind%in% levels(festgenrevecs$colorgenre)~txtKind, T~"...")) %>% 
  mutate(colorgenre2=fct_relevel(as.factor(colorgenre), 
                                levels(festgenrevecs$colorgenre) %>% gsub("other","...",.) %>% rev))

# festival illustration squares.
ggplot(tops, aes( x=s,y=libelleFestival_NEW_VZ, fill=colorgenre2))+
  geom_bar(stat="identity", color=NA,position="stack")+
  scale_fill_manual(values=sixgcols %>% rev)+
  coord_cartesian(expand = 0, xlim=c(0,100))+
  theme_void()+
  theme(axis.title = element_blank(),
        legend.position = "none",
        panel.border  = element_rect(size=0.5, color="gray10", fill=NA)
        )+
  facet_wrap(~libelleFestival_NEW_VZ, strip.position="bottom", scales = "free", nrow=2)

### 2023-02-19 index.Rmd
profile update

---
title: "Andres Karjus &nbsp;<font size='3'> evolutionary&nbsp;linguist | cultural&nbsp;data&nbsp;analytics&nbsp;scholar | digital&nbsp;humanities&nbsp;educator </font>"
output: 
  html_document: 
    theme: spacelab
    toc: no
    toc_depth: 4  
    toc_float:
      collapsed: no
---

@@

.twitter-timeline {
    height: 200px !important;
    overflow: scroll !important;
}

@@

<div class="container-fluid">
<div class="row">
  <div class="col-sm-7">
  <iframe src="news.html" width="100%" height="200" style="border: none;"></iframe>
  </div>
  <div class="col-sm-5">
  <a class="twitter-timeline" 
  data-show-screen-name="false" data-lang="en" 
  data-width="380px" 
  data-height="198px" 
  href="https://twitter.com/AndresKarjus?ref_src=twsrc%5Etfw"
  data-chrome="noheader nofooter">
  " "
  </a> 
<script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>
  </div>
</div>

@@

### What I do

<IMG SRC="IMG_2657.jpg" ALIGN="right" BR CLEAR="left" style="margin-left:10px; width: 49%; height: auto;">

<div style="text-align: justify; padding-left:1px"> 
I am a research fellow at the [CUDAN](http://cudan.tlu.ee/) Cultural Data Analytics lab at Tallinn University, working on **language and culture dynamics**, using large corpora, machine learning, and human experiments. Recently I have been also working on, through various collaborations, on art history and creative industries and advising collaborative projects between involving academic and media industry partners.<br>
I defended my PhD in 2020, in linguistics at the [Centre for Language Evolution](http://www.lel.ed.ac.uk/cle/) of University of Edinburgh, on lexical dynamics and communicative need in language.
I also occasionally teach **stats and data visualization** for the humanities and social sciences (see [more here](https://andreskarjus.github.io/artofthefigure)). The photo on the right is naturally slightly outdated, as is customary for academic home pages.

@@

## R workshops {#workshops}

If you're here about materials for an upcoming R or dataviz workshop: [click here](https://andreskarjus.github.io/artofthefigure/) to go to the dedicated workshops page.

@@

**Workshops**

- I have been developing teaching materials on data visualization using R, which I have used in over a dozen workshops for humanities and social science audiences since 2017, collectively under the title of [_aRt of the Figure_ (click here for more info)](https://andreskarjus.github.io/artofthefigure/). Some of these have been standalone events, some have been part of conferences, summer schools or academic retreats. All my materials are [open source](https://andreskarjus.github.io/artofthefigure/).

**Teaching**

- My postdoc includes some teaching activities, and I do occasional guest lectures; most recently for the Data Science and Digital Humanities programme at the University of Tartu and for the Cultural Data Analytics I and II courses at Tallinn University.

@@

Feel free to get in touch if you are interested in talking about organizing a workshop on anything related to data science and statistics, data visualization, R, corpus linguistics, natural language processing applications, digital humanities, etc.
</div>
<br>

@@

<div style="text-align: center; align:center"> 
<IMG SRC="round.jpg"> 
<br>
<br>
<br>
**Andres Karjus** <br> 
Research fellow, CUDAN Open Lab, Tallinn University <br>

>>>>

---
title: "Andres Karjus &nbsp;<font size='3'> evolutionary&nbsp;linguist | cultural&nbsp;data&nbsp;analytics&nbsp;scholar | digital&nbsp;humanities&nbsp;instructor </font>"
output: 
  html_document: 
    theme: spacelab
    toc: no
    toc_depth: 4  
    toc_float:
      collapsed: no
---

@@

<!-- .twitter-timeline { -->
<!--     height: 200px !important; -->
<!--     overflow: scroll !important; -->
<!-- } -->

@@

<div class="container-fluid">
<div class="row">
  <div class="col-sm-7">
  <iframe src="news.html" width="100%" height="200" style="border: none;"></iframe>
  </div>
  <div class="col-sm-5">
  <a class="twitter-timeline" 
  data-show-screen-name="false" 
  data-lang="en" 
  data-width="399px" 
  data-height="200px" 
  href="https://twitter.com/AndresKarjus?ref_src=twsrc%5Etfw"
  data-chrome="noheader nofooter">
  " "
  </a> 
<script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>
  </div>
</div>

@@

### What I do  <IMG SRC="round.jpg" ALIGN="right" BR CLEAR="left" style="margin-left:10px; width: 20%; height: auto;">
<div style="text-align: justify; padding-left:1px"> 
I am a research fellow at the [CUDAN](http://cudan.tlu.ee/) Cultural Data Analytics lab at Tallinn University, working on **language and culture dynamics**, using large corpora, machine learning, and human experiments. Recently I have been also working on, through various collaborations, on art history and creative industries and advising collaborative projects between involving academic and media industry partners.<br>
I defended my PhD in 2020, in linguistics at the [Centre for Language Evolution](http://www.lel.ed.ac.uk/cle/) of University of Edinburgh, on lexical dynamics and communicative need in language. <br>
I also occasionally do workshops on **R, stats & data visualization** and **AI**-related things (see [more here](https://datafigure.eu)).

@@

## R & AI workshops {#workshops}

I also teach workshops as an instructor in the private sector. 
Some of these have been standalone events, some have been part of conferences, summer schools or academic retreats. 
Feel free to get in touch if you are interested in talking about organizing a workshop on anything related to data science and statistics, artificial intelligence, data visualization, R, corpus linguistics, digital humanities, etc. <br>
For more details, head over to [datafigure.eu](https://datafigure.eu)

@@

**Academic teaching**

- My postdoc includes some teaching activities, and I do occasional guest lectures; recently for the Data Science and Digital Humanities programme at the University of Tartu and for the Cultural Data Analytics I and II courses at Tallinn University.

@@

</div>
<br>

@@

<div style="text-align: center; align:center"> 
<br>
<br>
<br>
**Andres Karjus** <br> 
PhD, MA (linguistics), MSc (artificial intelligence)

Research fellow, CUDAN Open Lab, Tallinn University <br>
Instructor at Datafigure OÜ
